Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-22 paper/sections/metis-language-and-proofs.tex
[ paper ] working on structurally smaller arguments.
[ paper ] improving the writing.

% % -*- root: main.tex -*-
\documentclass[../main.tex]{subfiles}
\begin{document}

@@

\textit{Output.}~\TSTP language is de facto output standard language
for derivations of ATPs~\cite{sutcliffe2004tstp}. A \TSTP derivation
is a directed acyclic graph, a proof tree, where each leaf is a
formula from the \TPTP input. A node is a formula inferred from the
parent formulas. The root is the final derived formula. Such a
derivation is a list of annotated formulas with the form.

@@

\textit{Simplification.}
The \simplify rule is an inference that performs simplification of
definitions or tautologies over a list of derivations. This rule
transverses a list of formulas by applying different theorems (e.g.,
\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
syllogism}) including the list of theorems used by \canonicalize in
Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
theorem of the \resolve rule.

Moreover, we are not completely sure about the exact behavior for
all \Metis' inference rules. It is somewhat complicated to grasp it
completely since the source code is around the 10.000 lines of code.

>>>>

%
\documentclass[../main.tex]{subfiles}
\begin{document}

@@

\textit{Output.}~\TSTP language is de facto output standard language
for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}. A \TSTP derivation
is a directed acyclic graph, a proof tree, where each leaf is a
formula from the \TPTP input. A node is a formula inferred from the
parent formulas. The root is the final derived formula. Such a
derivation is a list of annotated formulas with the form.

@@

\textit{Simplification.}
The \simplify rule is an inference that performs simplification of
definitions and tautologies. This rule
transverses a list of formulas by applying different theorems (e.g.,
\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
syllogism}) including the list of theorems used by \canonicalize in
Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
theorem of the \resolve rule.

Moreover, we are not completely covered every detail in the behavior
for all \Metis' inference rules. It is somewhat complicated to grasp
completely the inference rules since the source code is around the
10.000 lines of code.
